% This template is designed to offer an aesthetically pleasing resume that adheres to a formal and institutional tone, making it suitable for applications to companies and research centers requiring a high degree of professionalism. Navy blue has been chosen as the primary color to align with these objectives.
% The code is well-documented and annotated, allowing users to easily customize and modify it according to their needs. Please note that the template's content is meant to be humorous and should not be taken literally. We are grateful for your interest in using this template for your professional endeavors.
% Author: Christian Maria Giannetti

%----------------------------------------------------------------------------------------
%  Packages And Other Document Configurations
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

% Document margins
\usepackage{caption}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{longtable}

\DeclareCaptionLabelFormat{empty}{}
\captionsetup[longtable]{labelformat=empty, font=bf}
% Color and hyperlink packages
\usepackage{xcolor}
\usepackage{hyperref}

% Footnote and margin adjustment packages
\usepackage{footnote}
\usepackage{changepage}

% Fontawesome package for icons
\usepackage{fontawesome}

% Tabularx package for custom tables
\usepackage{tabularx}

% Define navyblue color
\definecolor{navyblue}{RGB}{0,54,123}

%----------------------------------------------------------------------------------------
%   Customizations
%----------------------------------------------------------------------------------------

% Define italicitem, bolditem, and plainitem commands
\newcommand{\italicitem}[1]{\item{\textit{#1}}}
\newcommand{\bolditem}[1]{\item{\textbf{#1}}}
\newcommand{\plainitem}[1]{\item{#1}}

% Define user-friendly link command for hyperlinks
\newcommand{\link}[2]{{\href{#1}{#2}}}

\newcommand{\entry}[2]{#1 & #2 \tabularnewline} % Defines an entry with two arguments: #1 for the first column and #2 for the second column

%----------------------------------------------------------------------------------------
%   Define envsection command for defining a new environment section
%----------------------------------------------------------------------------------------

\newcommand{\tableEnv}[2]{%
  \begin{rSection}{#1} % Begin rSection with the given name
    \begin{adjustwidth}{0.0in}{0.1in} % Set the left and right margins
      \begin{tabularx}{\linewidth}{@{} >{\bfseries}l @{\hspace{6ex}} X @{}}
        #2 % Print the content inside the tabularx environment
      \end{tabularx}
    \end{adjustwidth}
  \end{rSection}
}

%----------------------------------------------------------------------------------------
%   Begin document
%----------------------------------------------------------------------------------------

% Set name with navyblue color
\name{\color{navyblue} Vijayaraagavan S}

\begin{document}

\printPersonalInfo{
  \personalInfo{\tag{Residence/domicile}\info{Coimbatore}}
  \personalInfo{\tag{E-mail}\info{svijayaraagavan@gmail.com} \infoSeparator\tag{Mobile number}\info{+91-9344811811}}
  \personalInfo{\tag{LinkedIn}\info{\href{https://www.linkedin.com/in/vijayaraagavan-s-3849b3227/}{vijayaraagavan}} \tag{GitHub}\info{\href{https://github.com/Vijayaraagavan}{github.com/Vijayaraagavan}} 
  \infoSeparator\tag{Date of birth}\info{13-11-2000}}
}

%----------------------------------------------------------------------------------------
%   Education section
%----------------------------------------------------------------------------------------

\begin{rSection}{Career Objective}

    % Updated entry
    {Detail-oriented and highly skilled \textbf{Elixir and React developer} with 2 years of experience in building robust, scalable, and high-performance applications. Proficient in designing and implementing efficient back-end systems with Elixir and developing dynamic, user-friendly front-end interfaces using React. Strong problem-solving skills and a passion for writing clean, maintainable, and well-documented code.}

% \end{rSection}

    % \end{rSubsectionNoBullet}
    
\subsection*{Key Skills}

 \hspace{5mm} \textbf{Back-end Development:} Elixir (Phoenix), Golang

 \hspace{5mm} \textbf{Web Development:} Vue.js, React

 \hspace{5mm} \textbf{Database Management:} PostgreSQL, MongoDB

 \hspace{5mm} \textbf{CI/CD:} CircleCI

 \hspace{5mm} \textbf{Firebase Development:} Firebase

 \hspace{5mm} \textbf{Operating Systems:} Linux (Ubuntu)

 \hspace{5mm} \textbf{DevOps:} Docker, Kubernetes

 \hspace{5mm} \textbf{Scripting and Automation:} Bash Scripting, Postman

 % \hspace{5mm} \textbf{Design Tools:} Figma

 \hspace{5mm} \textbf{Programming Languages:} JavaScript, Java, Elixir, Golang.

\end{rSection}


%----------------------------------------------------------------------------------------
%   Work experience section
%----------------------------------------------------------------------------------------

\begin{rSection}{Work experience}

    % First work experience entry
    \begin{rSubsection}{Ardhika Software Technologies Pvt. Ltd.}{May 2022 - june 2024}{Software Engineer}{Chennai, India}
        \item Developed the Cloud-based Restaurant PoS application using Vue.js.
        \item Developed microservice-based servers in Elixir and Golang.
        \item Developed custom plugins to facilitate seamless communication between web app and native Android features using java
        % \item Streamlined internal meme generation pipelines.
    \end{rSubsection}

    \begin{rSubsection}{GetBeamer Pvt. Ltd.}{June 2024 - Present}{Software Development Engineer - 1}{Chennai, India}
        \item Contributed to the development of an onboarding software that enhances end-user onboarding experiences for customer websites using tooltips, modals, dialogs, and complex step-by-step tutorials.
        \item Designed and implemented scalable back-end systems using Phoenix (Elixir), GraphQL, Ecto, and managed asynchronous processing with Verk and Oban jobs.
        \item Integrated third-party tools such as Mixpanel, Intercom, and HubSpot to enhance user engagement and analytics capabilities.
        \item Built advanced analytical tools for generating detailed reports, leveraging PostgreSQL and ClickHouse for data storage and querying.
        \item Conducted multiple Proof of Concepts (POCs) for integrating new tools and technologies into the system.
        \item Created and customized dashboards in Grafana for monitoring and reporting purposes.
        \item Managed staging infrastructure using Terraform, Kubernetes, Cloudflare, and Google Secrets for secure and efficient deployments.
\end{rSubsection}

    
    % Second work experience entry
    % \begin{rSubsection}{Viral News Robotics Laboratory (VNRL)}{March 2019 - July 2019}{Robotics Comedian Intern}{Fries, Virginia}
    %     \item Engineered a robotic Tyrion Lannister that repeatedly asks, "Where's the wine?"
    % \end{rSubsection}
    
    % % Third work experience entry
    % \begin{rSubsection}{Library of Alexandria 2.0}{January 2017 - April 2018}{Novelist}{Cut and Shoot, Texas}
    %     \item Curated the "Dumb \& Dumber Guide to Classic Literature", featuring "Fifty Smudges 
    %     of Gray", "Pride and Prejudice: smart girls can always find a way to rationalize marrying for money"
    %     \item Hosted a weekly meme reading club on "Breadxit": the debate over whether bread should be banned from Europe
    % \end{rSubsection}
    
\end{rSection}

%----------------------------------------------------------------------------------------
% Technical skills section
%----------------------------------------------------------------------------------------
% \begin{rSection}{Technical skills}{
\begin{longtable}{lp{0.7\linewidth}}
    \caption{Technical Skills} \\
    \hline
    \textbf{Skill} & \textbf{Description} \\
    \hline
    \endfirsthead
    
    \hline
    \textbf{Skill} & \textbf{Description} \\
    \hline
    \endhead

    % Insert blank row with specified height
    \multicolumn{2}{c}{\rule{0pt}{10pt}} \\
    
    \entry{Web Development}{Skilled in building responsive and interactive web applications using \textbf{React} and Vue.js frameworks, including proficiency in the \textbf{Composition API and Vuetify}.} \\
    \entry{Database Management}{Proficient in designing and managing relational and non-relational databases, with expertise in \textbf{PostgreSQL} and \textbf{MongoDB}.} \\
    \entry{Back-end Development}{Experienced in back-end development using \textbf{Elixir} and \textbf{Golang}, leveraging their strengths in concurrency, scalability, and fault-tolerance.} \\
    \entry{CI/CD}{Proficient in \textbf{CircleCI}, utilizing it for automating the build, test, and deployment processes of software projects.} \\
    \entry{Operating Systems}{Proficient in \textbf{Linux operating systems}, including Ubuntu for server deployment and maintenance. Experienced in deploying web apps and API servers to Linux-based servers, ensuring smooth installation and configuration.} \\
    \entry{DevOps}{Proficient in containerization using \textbf{Docker}, facilitating consistent development and deployment environments. Familiar with Kubernetes for container orchestration and managing containerized applications in production environments.} \\
    \entry{Scripting and Automation}{Experienced in automating tasks using \textbf{Bash scripting}, streamlining repetitive processes and enhancing workflow efficiency. Proficient in writing chaining requests and \textbf{testing APIs using Postman}, ensuring the reliability and functionality of web services.} \\
    \entry{Programming Languages}{JavaScript, Java, Elixir, Golang} \\
\end{longtable}


% %----------------------------------------------------------------------------------------
% % Memberships section
% %----------------------------------------------------------------------------------------

% \tableEnv{Projects}{
% \entry{Databox}{a cloud-based storage service that enables users to store and access files online}
%     \entry{Super Pocket app}{A multi purpose, daily usage app written in Flutter}
%     \entry{Pos Median}{An intermediate server that establishes connection between two servers using websocket written in Elixir}
    
% }
\section*{Projects}

\subsection*{Restaurant POS Application}

\textbf{Description:} Contributed to the development of a comprehensive Restaurant POS (Point of Sale) application with a focus on modernizing and streamlining restaurant operations. The application facilitates efficient order management, payment processing, and customer interaction.

\textbf{Key Contributions:}
\begin{itemize}
    \item Collaborated in developing the user interface (UI) of the application using Vue.js, ensuring a responsive and intuitive experience for restaurant staff.
    \item Assisted in building a centralized server using Golang to handle core business logic and database operations, ensuring scalability and performance.
    \item Contributed to the development of an offline server in Elixir to support seamless operation even in the absence of internet connectivity, ensuring uninterrupted service.
    \item Played a key role in implementing a median server in Elixir that establishes connections between two servers and the client web application, enabling real-time communication and data synchronization.
    \item Participated in the development of a contactless ordering application for customers, allowing them to browse the menu and place orders from their smartphones, enhancing convenience and safety.
\end{itemize}

\textbf{Technologies Used:} Vue.js, Golang, Elixir, WebSockets, RESTful APIs

\subsection*{Userflow}

\textbf{Description:} Built "Userflow," a comprehensive onboarding solution that simplifies end-user onboarding for customer websites through interactive tutorials featuring tooltips, modals, dialogs, and multi-step workflows.

\textbf{Key Features:}
\begin{itemize}
    \item Architected a scalable back-end system using Phoenix (Elixir) with GraphQL and Ecto to enable seamless data handling and API integrations.
    \item Implemented background job processing pipelines with Verk and Oban to support efficient task execution and improved system performance.
    \item Integrated with leading analytics and customer engagement platforms, including Mixpanel, Intercom, and HubSpot, to enhance insights and tracking capabilities.
    \item Engineered advanced reporting tools by combining the capabilities of PostgreSQL and ClickHouse for real-time and historical data analysis.
    \item Developed custom dashboards in Grafana to monitor application performance and provide actionable insights.
    \item Deployed and maintained staging environments using Terraform, Kubernetes, Cloudflare, and Google Secrets to ensure secure and reliable infrastructure management.
    \item Evaluated and integrated cutting-edge tools and technologies through multiple Proof of Concept (POC) implementations.
\end{itemize}

\textbf{Technologies Used:} Phoenix (Elixir), GraphQL, Ecto, PostgreSQL, ClickHouse, Verk, Oban, Grafana, Terraform, Kubernetes, Cloudflare


% \subsection*{Split Bill Application}

% \textbf{Description:} Developed a Split Bill application using Vue.js framework for the frontend and Firebase for backend services. The application allows users to split expenses between multiple people efficiently.

% \textbf{Key Features:}
% \begin{itemize}
%     \item Implemented user authentication and authorization using Firebase Authentication, ensuring secure access to the application.
%     \item Utilized Firebase Realtime Database to store and manage expense data, enabling real-time synchronization across multiple devices.
%     \item Designed an intuitive user interface with Vue.js, allowing users to easily add expenses, specify contributors, and view detailed summaries.
% \end{itemize}

% \textbf{Technologies Used:} Vue.js, Firebase (Realtime Database, Authentication), HTML, CSS
%----------------------------------------------------------------------------------------

%   Extracurricular activities section
%----------------------------------------------------------------------------------------

% \begin{rSection}{Extracurricular activities}

% % First extracurricular entry
% \begin{rSubsectionNoBullet}{Hobbee Club: Self teaching for Laziness}{2018 - 2020}{Teaching Web development to enthusiastic students}{Chennai}
%     \plainitem{}
% \end{rSubsectionNoBullet}

% \end{rSection}

\begin{rSection}{Education}

    % Master's degree entry
    % \begin{rSubsectionNoBullet}{\bf Bachelor's degree in Electrical and Electronics Engineering}{College of Engineering Guindy, Anna university- Chennai }{Bachelor's degree program}{May 2017 - April 2021}
    %     \italicitem{Graduated with honors}
    %     % \italicitem{Thesis title: A deep learning approach to predicting the next Brexit: Unicorns vs. White Walkers}
    % \end{rSubsectionNoBullet}
    
    % Bachelor's degree entry
    \begin{rSubsectionNoBullet}{\bf Bachelor's degree in Electrical and Electronics Engineering}{College of Engineering Guindy, Anna university- Chennai }{Bachelor's degree program}{May 2017 - April 2021}
        \italicitem{Final grade: 7.6/10}
    \end{rSubsectionNoBullet}

\end{rSection}

% Language proficiencies section
%----------------------------------------------------------------------------------------

\tableEnv{Language proficiencies}{
    \entry{English}{Fluent in speaking and writing}
    \entry{Tamil}{Proficient}
}

%----------------------------------------------------------------------------------------

% %----------------------------------------------------------------------------------------
% % Most relevant projects section
% %----------------------------------------------------------------------------------------

% \tableEnv{Portfolio of most relevant projects}{
%     \entry{Survey}{Analyzing the effects of replacing office chairs with unicycles on employee morale}
%     \entry{Survey}{Investigation of the therapeutic effects of watching cat videos for 8 hours a day}
%     \entry{Paper}{The correlation between sock loss in laundry and the existence of parallel universes}
%     \entry{Article}{The definitive study on the impact of pineapple as a pizza topping on global diplomacy}
% }


\end{document}
